Equalizer\\Programming and User Guide

### 2011-02-14 Developer/ProgrammingGuide/paper.tex
Improve statistics overlay: - Improve readability of compression ratios - Add downloader and compressor plugin name (uploader missing for now) Add return value to image readback Documentation updates
[ ] May break build
[ ] May break existing applications (see CHANGES.txt)
[ ] Bugfix
[x] New Feature
[x] Cleanup
[ ] Optimization
[ ] Documentation

{\footnotesize\lstinputlisting[firstline=90, lastline=101]
  {../../../src/examples/eqPly/eqPly.cpp}}

@@

{\footnotesize\lstinputlisting[firstline=103, lastline=118]
  {../../../src/examples/eqPly/eqPly.cpp}}

>>>>

{\footnotesize\lstinputlisting[firstline=90, lastline=100]
  {../../../src/examples/eqPly/eqPly.cpp}}

@@

{\footnotesize\lstinputlisting[firstline=101, lastline=118]
  {../../../src/examples/eqPly/eqPly.cpp}}
